Longer term All-Cause and Cardiovascular Mortality with Intensive Blood Pressure Control

### 2022-03-02 index.Rmd
putting slides in the pipe

@@

source("packages.R")

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600, 
                      fig.width = 10, 
                      fig.height = 8)

@@

```{r}

fig$inc_acm[[1]]

>>>>

# IN CASE YOU NEED THIS IN PDF: Run this code in console:
# pagedown::chrome_print('index.html')
# But avoid using the pdf version when you present b/c you 
# can access keyboard shortcuts if you present from html.
# e.g., presenter mode by pressing 'p'

@@

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600)

@@

```{r fig.width = 10, fig.height = 8}

fig$inc_cvd[[1]] + 
  theme(legend.key.size = unit(1.2, 'cm'), #change legend key size
        legend.key.height = unit(1.2, 'cm'), #change legend key height
        legend.key.width = unit(1.2, 'cm'), #change legend key width
        legend.title = element_text(size=16), #change legend title font size
        legend.text = element_text(size=16)) #change legend text font size
